Automating Verification of MPC Security

### 2023-06-20 popl24/bruteforce.tex
typos bruteforce.tex

We have shown how our formulation of program distributions, a precise
definition of intensional protocol behavior, can be used to enforce
the extensional property of MPC security. This intensional description
also has the benefit of being flexible- we can use the same mechanisms
to desribe $\NIMO$, noninterference, perfect secrecy, violations of
obliviousness, etc. These mechanisms can also be exploited to support
automated program analysis.

We initially explore a brute force approach to automatically verifying
program behaviour, the first step of which is to compute the basic
distribution of a program $\prog$. The program distribution
$\progd(\prog)$ can obviously be automatically derived from that, as
can be any of its marginal or conditional distributions. In this
Section we consider two automated mechanisms for deriving
$\progd(\prog)$ in this way. The first is through a straightforward
computation of all final program memories.  The second approach
rewrites $\minifed$ programs to stratified Datalog programs, that are
amenable HPC optimizations such as parallelization and GPU matrix
computations as shown in recent work
\cite{sakama2017linear,aspis2018linear,nguyen2022enhancing,nguyen2021efficient}.

@@

We have used the code for $\cruns$ and $\cprogd$ extensively to design and
verify the examples in this paper. We will discuss other examples in
Section \ref{section-composition}, but here we note that we've verified
passive security of Examples \ref{example-he} and \ref{example-OT}-
for the former this is well-known so the result is a simple proof-of-concept,
but the latter is a new (though unsurprising) result, having not been
directly proven in \cite{barthe2019probabilistic}. The method for
verifying $\NIMO$ described here generalizes to any $\prog$. 
\begin{lemma}[Automated Verification of Passive Security]
  \label{lemma-bruteforce-nimo}
  $\prog_{\ref{example-he}}$ and $\prog_{\ref{example-OT}};\eassign{\outv}{\vx{2}{mc}}$ are
  passive secure.
\end{lemma}
\begin{proof}
  For both $\prog \in \{
  \prog_{\ref{example-he}},\prog_{\ref{example-OT}};\eassign{\outv}{\vx{2}{mc}}\}$
  we compute $\cruns(\prog)$ and $\cprogd(\prog)$ and then verify
  $\NIMO(\prog)$ using the following algorithm. Given $\iov(\prog) = S
  \cup V$ and $\flips(\prog) = F$, we enumerate all memories $\store
  \in \cruns(\prog)$, then enumerate all partitions of clients into
  sets $H$,$C$ such that $|C| \le |H|$ and $0 \in C$, and then check:
  $$
  \cprogd(\prog)(\store_{S_H}|\store_{S_C \cup \{\outv\}}) =
  \cprogd(\prog)(\store_{S_H}|\store_{S_C \cup V_C})
  $$
  for each $H,C,\store$. The result follows by Lemma \ref{lemma-cprogd}, Lemma \ref{lemma-nimo}, and
  Theorem \ref{theorem-nimo}.
\end{proof}

>>>>

We have shown how our formulation of program distributions, a precise
definition of intensional protocol behavior, can be used to enforce
the extensional property of MPC security. This intensional description
also has the benefit of being flexible- we can use the same mechanisms
to describe $\NIMO$, noninterference, perfect secrecy, violations of
obliviousness, etc. These mechanisms can also be exploited to support
automated program analysis.

We initially explore a brute force approach to automatically verifying
program behaviour, the first step of which is to compute the basic
distribution of a program $\prog$. The program distribution
$\progd(\prog)$ can obviously be automatically derived from that, as
can be any of its marginal or conditional distributions. In this
Section, we consider two automated mechanisms for deriving
$\progd(\prog)$ in this way. The first is through a straightforward
computation of all final program memories.  The second approach
rewrites $\minifed$ programs to stratified Datalog programs, that are
amenable HPC optimizations such as parallelization and GPU matrix
computations as shown in recent work
\cite{sakama2017linear,aspis2018linear,nguyen2022enhancing,nguyen2021efficient}.

@@

We have used the code for $\cruns$ and $\cprogd$ extensively to design and
verify the examples in this paper. We will discuss other examples in
Section \ref{section-composition}, but here we note that we've verified
passive security of Examples \ref{example-he} and \ref{example-OT}-
for the former, this is well-known so the result is a simple proof-of-concept,
but the latter is a new (though unsurprising) result, having not been
directly proven in \cite{barthe2019probabilistic}. The method for
verifying $\NIMO$ described here generalizes to any $\prog$. 
\begin{lemma}[Automated Verification of Passive Security]
  \label{lemma-bruteforce-nimo}
  $\prog_{\ref{example-he}}$ and $\prog_{\ref{example-OT}};\eassign{\outv}{\vx{2}{mc}}$ are
  passive secure.
\end{lemma}
\begin{proof}
  For both $\prog \in \{
  \prog_{\ref{example-he}},\prog_{\ref{example-OT}};\eassign{\outv}{\vx{2}{mc}}\}$
  we compute $\cruns(\prog)$ and $\cprogd(\prog)$ and then verify
  $\NIMO(\prog)$ using the following algorithm. Given $\iov(\prog) = S
  \cup V$ and $\flips(\prog) = F$, we enumerate all memories $\store
  \in \cruns(\prog)$, then enumerate all partitions of clients into
  sets $H$,$C$ such that $|C| \le |H|$ and $0 \in C$, and then check:
  $$
  \cprogd(\prog)(\store_{S_H}|\store_{S_C \cup \{\outv\}}) =
  \cprogd(\prog)(\store_{S_H}|\store_{S_C \cup V_C})
  $$
  for each $H,C,\store$. The result follows by Lemma \ref{lemma-cprogd}, Lemma \ref{lemma-nimo}, and
  Theorem \ref{theorem-nimo}.
\end{proof}
